Figure 7 - heterodimer

### 2024-07-09 ms_figure_7_heterodimer.Rmd
Add axis titles for coverage plots (Fig 7)

## Correlation between log2 fold changes for ntu1/ntu2
stopifnot(all(rownames(resList$ntu1) == rownames(resList$ntu2)))
dfcorr <- data.frame(gene = rownames(resList$ntu1), 
                     ntu1 = resList$ntu1$log2FoldChange,
                     ntu2 = resList$ntu2$log2FoldChange)
corrplot <- list(
    ggplot(dfcorr, aes(x = ntu1, y = ntu2)) + 
        geom_abline(slope = 1, intercept = 0, linetype = "dashed", 
                    color = "grey50") + 
        geom_point(alpha = 0.25) + 
        geom_text_repel(data = dfcorr |>
                            dplyr::filter(gene %in% c("tna1", "SPCC576.17c")), 
                        aes(label = gene), 
                        min.segment.length = 0, max.overlaps = Inf) + 
        labs(x = "*ntu1\U141E* log2(fold-change)",
             y = "*ntu2\U141E* log2(fold-change)") + 
        theme_cowplot() + 
        theme(axis.title = element_markdown())
)

@@

@@

    scale_y_continuous(limits = c(0, 0.9), expand = c(0, 0))

@@

    scale_fill_manual(values = c(wt = lighten("black", amount = 0.4), 
                                 "ntu1\U141E" = lighten(main_colors[5], amount = 0.4), 
                                 "ntu2\U141E" = lighten(main_colors[1], amount = 0.4))) + 

@@

    scale_y_continuous(limits = c(-0.9, 0.3), expand = c(0, 0))

@@

                               strip.text.x = element_text(size = 12, hjust = 0.95)), 

@@

                               strip.text.x = element_blank()), 

@@

fig7c <- wrap_plots(maplots, ncol = 1) | corrplot[[1]]

@@

cowplot::plot_grid(
    figs6a,
    cowplot::plot_grid(
        p_rel_dis,
        genomeplot_tpm,
        nrow = 1, 
        rel_widths = c(1, 1), 
        labels = c("B", "C")
    ),
    cowplot::plot_grid(
        genomeplot,
        gcovdel,
        # maplots$ID83delTMD,
        nrow = 1, 
        rel_widths = c(1, 1),
        labels = c("C", "E")
    ),
    ncol = 1, rel_heights = c(1, 1, 1)
)
```

>>>>

@@

```{r}
#| label: rnaseq-corrplot

## Correlation between log2 fold changes for ntu1/ntu2
stopifnot(all(rownames(resList$ntu1) == rownames(resList$ntu2)))
dfcorr <- data.frame(gene = rownames(resList$ntu1), 
                     ntu1 = resList$ntu1$log2FoldChange,
                     ntu2 = resList$ntu2$log2FoldChange)
(corrplot <- list(
    ggplot(dfcorr, aes(x = ntu1, y = ntu2)) + 
        geom_abline(slope = 1, intercept = 0, linetype = "dashed", 
                    color = "grey50") + 
        geom_point(alpha = 0.25) + 
        geom_text_repel(data = dfcorr |>
                            dplyr::filter(gene %in% c("tna1", "SPCC576.17c")), 
                        aes(label = gene), 
                        min.segment.length = 0, max.overlaps = Inf) + 
        labs(x = "*ntu1\U141E* log2(fold-change)",
             y = "*ntu2\U141E* log2(fold-change)") + 
        theme_cowplot() + 
        theme(axis.title = element_markdown())
))
```

@@

    scale_y_continuous(limits = c(0, 0.9), expand = c(0, 0)) + 
    labs(y = "ChIP-seq")

@@

    scale_fill_manual(values = c(wt = "black", 
                                 "ntu1\U141E" = main_colors[5], 
                                 "ntu2\U141E" = main_colors[1])) + 

@@

    scale_y_continuous(limits = c(-0.9, 0.3), expand = c(0, 0)) + 
    labs(y = "RNA-seq")

@@

                               strip.text.x = element_text(size = 12, hjust = 0.95),
                               axis.title.y = element_text(size = 12, angle = 90,
                                                           margin = margin(t = 0, r = 10, b = 0, l = 0))), 

@@

                               strip.text.x = element_blank(),
                               axis.title.y = element_text(size = 12, angle = 90,
                                                           margin = margin(t = 0, r = 15, b = 0, l = 0))), 

@@

fig7c <- wrap_plots(maplots, ncol = 2)

@@

cowplot::plot_grid(
    figs6a,
    cowplot::plot_grid(
        p_rel_dis,
        genomeplot_tpm,
        nrow = 1, 
        rel_widths = c(1, 1), 
        labels = c("B", "C")
    ),
    cowplot::plot_grid(
        genomeplot,
        gcovdel,
        # maplots$ID83delTMD,
        nrow = 1, 
        rel_widths = c(1, 1),
        labels = c("D", "E")
    ),
    ncol = 1, rel_heights = c(1, 1, 1)
)
```
